sensiAnPaper1All

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50.Rmd
shorten effectiveness var names

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='black', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='red', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='red', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='black')
           )

  # doing the lm outside of ggplot    
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

@@

             theme_bw() +
             theme(legend.position = "bottom") +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             #geom_smooth(data=df_same, method = "lm", se = FALSE)
             #todo change to where exactly 20% diff
             geom_smooth(data=df_20pc, method = "lm", se = FALSE,colour='red', lwd=0.5)+
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=df_20pc, size=0.8, colour='red', shape=2) #, fill='white') 
           )

  # doing the lm outside of ggplot    
  x1=df_20pc$exposure 
  y1=df_20pc$effectiveness_insecticide1 + df_20pc$effectiveness_insecticide2

@@

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='black', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='red', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='red', shape=2, fill='white') +

             #now add the unequal points
             #showed that they were on both sides
             #geom_point(data = unequal, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=2) +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='black')
           )

  # doing the lm outside of ggplot    
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

>>>>

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_ins1",
  #             "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  in_cols <- c("exposure","effectiveness_ins1","dominance_allele1")

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_diff, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_diff))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='black', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='red', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='red', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_ins1 + effectiveness_ins2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='black')
           )

  # doing the lm outside of ggplot    
  x1=df_same$exposure 
  y1=df_same$effectiveness_ins1 + df_same$effectiveness_ins2

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_diff))+

@@

             theme_bw() +
             theme(legend.position = "bottom") +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             #geom_smooth(data=df_same, method = "lm", se = FALSE)
             #todo change to where exactly 20% diff
             geom_smooth(data=df_20pc, method = "lm", se = FALSE,colour='red', lwd=0.5)+
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=df_20pc, size=0.8, colour='red', shape=2) #, fill='white') 
           )

  # doing the lm outside of ggplot    
  x1=df_20pc$exposure 
  y1=df_20pc$effectiveness_ins1 + df_20pc$effectiveness_ins2

@@

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_diff))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='black', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='red', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='red', shape=2, fill='white') +

             #now add the unequal points
             #showed that they were on both sides
             #geom_point(data = unequal, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=2) +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_ins1 + effectiveness_ins2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='black')
           )

  # doing the lm outside of ggplot    
  x1=df_same$exposure 
  y1=df_same$effectiveness_ins1 + df_same$effectiveness_ins2

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
shorten effectiveness var names

  ####################
  #23/6/2016 experimenting to see if can reduce the % excluded by tweaking input ranges
  #20%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005, ]
  #16%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005, ]
  #18%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$exposure > 0.25, ]
  #16%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$exposure > 0.3, ]
  #7%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005 & dif_mix2_seq$exposure > 0.25, ]   
  #5%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005 & dif_mix2_seq$exposure > 0.3, ] 
  #26%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_insecticide1 > 0.4 & dif_mix2_seq$effectiveness_insecticide2 > 0.4, ]
  #13%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_insecticide1 > 0.4 & dif_mix2_seq$effectiveness_insecticide2 > 0.4 & dif_mix2_seq$exposure > 0.3, ]
  #10%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3, ] 
  #8%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_insecticide1 > 0.4 & dif_mix2_seq$effectiveness_insecticide2 > 0.4 & dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3, ] 
  #22%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$dominance_allele1 > 0.1 & dif_mix2_seq$dominance_allele2 > 0.1, ] 
  #5%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3 & dif_mix2_seq$dominance_allele1 > 0.1 & dif_mix2_seq$dominance_allele2 > 0.1, ]

@@

  # create added columns for effectiveness and dominance
  ggSubset$effectiveness_added <- ggSubset$effectiveness_insecticide1 + ggSubset$effectiveness_insecticide2
  ggSubset$dominance_added <- ggSubset$dominance_allele1 + ggSubset$dominance_allele2

  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  #in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")  
  in_cols <- c("exposure","effectiveness_added","dominance_added")

@@

  #BEWARE that this sets 0s (where mix & sequence are equal) to NA
  ggSubset$l_mod_confusion <- 
    ifelse ( (ggSubset$effectiveness_insecticide1+ggSubset$effectiveness_insecticide2) > ggSubset$l_mod_eff,
               ifelse(ggSubset$mixA_minus_seq0.5>0,"TP",ifelse(ggSubset$mixA_minus_seq0.5<0,"FP",NA))

@@

  #BEWARE that this sets 0s (where mix & sequence are equal) to NA
  ggSubset$l_mod_confusion <- 
    ifelse ( (ggSubset$effectiveness_insecticide1+ggSubset$effectiveness_insecticide2) > ggSubset$l_mod_eff,
               ifelse(ggSubset$mixA_not20pc_better_seq0.5==0,"TP",ifelse(ggSubset$mixA_not20pc_better_seq0.5==1,"FP",NA))

>>>>

  ####################
  #23/6/2016 experimenting to see if can reduce the % excluded by tweaking input ranges
  #20%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005, ]
  #16%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005, ]
  #18%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$exposure > 0.25, ]
  #16%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$exposure > 0.3, ]
  #7%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005 & dif_mix2_seq$exposure > 0.25, ]   
  #5%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005 & dif_mix2_seq$exposure > 0.3, ] 
  #26%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_ins1 > 0.4 & dif_mix2_seq$effectiveness_ins2 > 0.4, ]
  #13%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_ins1 > 0.4 & dif_mix2_seq$effectiveness_ins2 > 0.4 & dif_mix2_seq$exposure > 0.3, ]
  #10%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3, ] 
  #8%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_ins1 > 0.4 & dif_mix2_seq$effectiveness_ins2 > 0.4 & dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3, ] 
  #22%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$dominance_allele1 > 0.1 & dif_mix2_seq$dominance_allele2 > 0.1, ] 
  #5%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3 & dif_mix2_seq$dominance_allele1 > 0.1 & dif_mix2_seq$dominance_allele2 > 0.1, ]

@@

  # create added columns for effectiveness and dominance
  ggSubset$effectiveness_added <- ggSubset$effectiveness_ins1 + ggSubset$effectiveness_ins2
  ggSubset$dominance_added <- ggSubset$dominance_allele1 + ggSubset$dominance_allele2

  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_ins1",
  #             "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  #in_cols <- c("exposure","effectiveness_ins1","dominance_allele1")  
  in_cols <- c("exposure","effectiveness_added","dominance_added")

@@

  #BEWARE that this sets 0s (where mix & sequence are equal) to NA
  ggSubset$l_mod_confusion <- 
    ifelse ( (ggSubset$effectiveness_ins1+ggSubset$effectiveness_ins2) > ggSubset$l_mod_eff,
               ifelse(ggSubset$mixA_minus_seq0.5>0,"TP",ifelse(ggSubset$mixA_minus_seq0.5<0,"FP",NA))

@@

  #BEWARE that this sets 0s (where mix & sequence are equal) to NA
  ggSubset$l_mod_confusion <- 
    ifelse ( (ggSubset$effectiveness_ins1+ggSubset$effectiveness_ins2) > ggSubset$l_mod_eff,
               ifelse(ggSubset$mixA_not20pc_better_seq0.5==0,"TP",ifelse(ggSubset$mixA_not20pc_better_seq0.5==1,"FP",NA))

### 2016-06-27 inst/documents/sensiAnPaper1All.Rmd
shorten effectiveness var names

  #subsetting now done above before names prettified
  #treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','effectiveness_insecticide1','effectiveness_insecticide2','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #treeInput <- treeInput[ treePredictors, ]

>>>>

  #subsetting now done above before names prettified
  #treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','effectiveness_ins1','effectiveness_ins2','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #treeInput <- treeInput[ treePredictors, ]
